D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-09 ootavacuous.tex
Peter Sewell December 9 feedback, second installment
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\subsection{OOTA Definition}
\label{sec:OOTA Definition}

Prior work defines ``OOTA cycle'' by example, without a precise
definition.
Sometimes ``causal cycle'' is used as if it was a definition, but
without a clear decision process for what does and does not
constitute a causal cycle.
P0442R0 defines an OOTA cycle as a fixed-point computation that is
destroyed by perturbations, which makes perfect sense to that paper's
authors, but has left others unsatisfied.

@@

There are also many other tools, but failing that, it is always possible
to fall back to the oldest software-verification tool, namely manual
code inspection.

>>>>

\subsection{On OOTA Definitions}
\label{sec:On OOTA Definitions}

Prior work defines ``OOTA cycle'' by example, without a precise
definition.
Sometimes ``causal cycle'' is used as if it was a definition, but
without a clear decision process for what does and does not
constitute a causal cycle.
P0442R0 defines an OOTA cycle as a fixed-point computation that is
destroyed by perturbations, which makes perfect sense to that paper's
authors, but has left others unsatisfied.
Still others argue (perhaps correctly) that it is impossible to provide
a general definition of ``OOTA cycle'', but even accepting this raises
the question of whether a \emph{useful} definition can be formulated.

@@

There are also many other tools, but failing that, it is always possible
to fall back to older software-verification tools such as manual
code inspection.
